### 2017-11-28 paper/sections/5_file-systems.tex
add prefetching reference
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

%- memory utilization/heuristics
From a high-level the cache management policy we designed in
Figure~\ref{src:lru-dyn} trims the cache if the cache reaches a certain size
{\it and} if it has already absorbed the initial burstiness of the workload.
Much of this implementation was inspired by the file system metadata load
balancing policy in Figure~\ref{src:lua-cephfs}, which was presented
in~\cite{sevilla:sc15-mantle}. That policy migrates file system metadata if the
load is higher than the average load in the cluster {\it and} the current
server has been overloaded for more than two iterations. The two policies have
the following in common:

@@

\textbf{State Persisted Across Decisions} (Fig.~\ref{src:lru-dyn}: Lines 4,6;
Fig~\ref{src:lua-cephfs}: Lines 3,4,9) - these lines use Mantle to write/read state
from previous decisions.  For ParSplice, we save a boolean that indicates
whether we have absorbed the workload's initial burstiness. For CephFS, we save
the number of consecutive instances that the server has been overloaded. We
also clear the count (Line 10) if the server is no longer overloaded.

@@

These similarities among effective policies for two very different domains
suggests that the heuristics and techniques in other load balancers can be used
for cache management. The result suggests that the concepts and problems that
architects grapple with are transcendent and the solutions they design can be
re-used in different code bases.

@@

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/trace-atime.png}\\
\caption{File system metadata reads for a Lustre trace collected at LANL. The
vertical lines are the access patterns detected by the ParSplice cache
management policy from Section~\S\ref{sec:dom-specific}.
\label{fig:trace-atime}}
\end{figure}

@@

  \item Batching: how many operations to group together, when to send large
batches of updates. We could use Mantle to implement to the pathname leases from
IndexFS~\cite{ren:sc2014-indexfs} or the capabilities from
CephFS\footnote{http://docs.ceph.com/docs/master/cephfs/capabilities/}.

>>>>

%- memory utilization/heuristics
From a high-level the cache management policy we designed in
Figure~\ref{src:lru-dyn} trims the cache if the cache reaches a certain size
{\it and} if it has already absorbed the initial burstiness of the workload.
Much of this implementation was inspired by the CephFS metadata load
balancing policy in Figure~\ref{src:lua-cephfs}, which was presented
in~\cite{sevilla:sc15-mantle}. That policy migrates file system metadata if the
load is higher than the average load in the cluster {\it and} the current
server has been overloaded for more than two iterations. The two policies have
the following in common:

@@

\textbf{State Persisted Across Decisions} (Fig.~\ref{src:lru-dyn}: Lines 4,6;
Fig~\ref{src:lua-cephfs}: Lines 3,4,9) - these lines use Mantle to write/read state
from previous decisions.  For ParSplice, we save a boolean that indicates
whether we have absorbed the workload's initial burstiness. For CephFS, we save
the number of consecutive instances that the server has been overloaded. We
also clear the count (Line 9) if the server is no longer overloaded.

@@

These similarities among effective policies for two very different domains
suggest that the heuristics and techniques in other load balancers can be used
for cache management. The result support the notion that concepts and problems
that architects grapple with are transcendent and the solutions they design can
be re-used in different code bases.

@@

\begin{figure}[t]
\noindent\includegraphics[width=0.5\textwidth]{figures/trace-atime.png}\\
\caption{File system metadata reads for a Lustre trace collected at LANL. The
vertical lines are the access patterns detected by the ParSplice cache
management policy from Section~\S\ref{sec:dom-specific}. The policy works
``out-of-the-box", which suggests that data management policies are general and
can be used across domains.
\label{fig:trace-atime}}
\end{figure}

@@

  \item Batching: how many operations to group together, when to send large
batches of updates. We could use Mantle to implement pathname leases from
IndexFS~\cite{ren:sc2014-indexfs} or the capabilities from
CephFS\footnote{http://docs.ceph.com/docs/master/cephfs/capabilities/}.

### 2017-11-28 paper/sections/6_conclusion.tex
add prefetching reference
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

State-of-the-art distributed file systems partition write-heavy workloads and
replicate read-heavy workloads, similar to the approach we are advocating
here.  IndexFS~\cite{ren:sc2014-indexfs} partitions directories and clients
write to different partitions by grabbing leases and caching ancestor metadata
for path traversal. ShardFS takes the replication approach to the extreme by
copying all directory state to all nodes. The Ceph file system
(CephFS)~\cite{weil:sc2004-dyn-metadata, weil:osdi2006-ceph} employs both
techniques to a lesser extent; directories can be replicated or sharded but the
caching and replication policies are controlled with tunable parameters.  These
systems still need to be tuned by hand with {\it ad-hoc} policies designed for
specific applications.  Setting policies for migrations is arguably more
difficult than adding the migration mechanisms themselves.  For example,
IndexFS/CephFS use the GIGA+~\cite{patil:fast2011-giga} technique for
partitioning directories at a \emph{predefined} threshold. Mantle makes headway
in this space by providing a framework for exploring these policies, but does
not attempt anything more sophisticated ({\it e.g.}, machine learning) to create
these policies.

@@

Data management encompasses a wide range of techniques that vary by application
and storage system.  Yet, the techniques require policies that shape the
decision making and finding the best policies is a difficult, multi-dimensional
problem.  We iterate to a custom solution for our target application that uses
workload access patterns to size its caches. Without tuning or parameter
sweeps, our solution saves memory without sacrificing performance for a variety
of initial conditions, including the scale, duration, configuration, and
hardware of the simulation. More importantly, rather than attempting to
construct a single, complex policy that works for a variety of scenarios, we
instead use the Mantle framework to enable software-defined storage systems to
flexibly change policies as the workload changes.  We also observe that many of
the primitives and strategies have enough in common with data management in
file systems that they both can be expressed with similar semantics and a
general policy engine.

This lays the foundation for future work, where we will focus on formalizing a
collection of general data management policies that can be used across
applications and storage systems.  The value of such a collection eases the
burden of policy development and paves the way for solutions that remove the
administrator from the development cycle, such as (1) adaptable policies that
automatically switch to new strategies when the current strategy behaves poorly
({\it e.g.}, thrashing, making no progress, etc.), and (2) policy generation,
where new policies are constructed automatically by examining the collection of
existing policies.  Ultimately, we hope that this automation enables control of
policies by machines instead of administrators.

>>>>

State-of-the-art distributed file systems partition write-heavy workloads and
replicate read-heavy workloads, similar to the approach we are advocating here.
IndexFS~\cite{ren:sc2014-indexfs} partitions directories and clients write to
different partitions by grabbing leases and caching ancestor metadata for path
traversal. ShardFS~\cite{xiao:socc15-shardfs} takes the replication approach to
the extreme by copying all directory state to all nodes.
CephFS~\cite{weil:sc2004-dyn-metadata, weil:osdi2006-ceph} employs both
techniques to a lesser extent; directories can be replicated or sharded but the
caching and replication policies are controlled with tunable parameters.  These
systems still need to be tuned by hand with {\it ad-hoc} policies designed for
specific applications.  Setting policies for migrations is arguably more
difficult than adding the migration mechanisms themselves.  For example,
IndexFS/CephFS use the GIGA+~\cite{patil:fast2011-giga} technique for
partitioning directories at a \emph{predefined} threshold. Mantle makes headway
in this space by providing a framework for exploring these policies, but does
not attempt anything more sophisticated ({\it e.g.}, machine learning) to
create these policies.

@@

Data management encompasses a wide range of techniques that vary by application
and storage system.  Yet, the techniques require policies that shape the
decision making and finding the best policies is a difficult, multi-dimensional
problem.  We iterate to a custom solution for our target application that uses
workload access patterns to size its caches. Without tuning or parameter
sweeps, our solution saves memory without sacrificing performance for a variety
of initial conditions, including the scale, duration, configuration, and
hardware of the simulation. More importantly, rather than attempting to
construct a single, complex policy that works for a variety of scenarios, we
instead use the Mantle framework to enable software-defined storage systems to
flexibly change policies as the workload changes.  We also observe that many of
the primitives and strategies have enough in common with data management in
file systems that they both can be expressed with similar semantics.

This lays the foundation for future work, where we will focus on formalizing a
collection of general data management policies that can be used across
applications and storage systems.  The value of such a collection eases the
burden of policy development and paves the way for automated solutions such as
(1) adaptable policies that switch to new strategies when the current strategy
behaves poorly ({\it e.g.}, thrashing, making no progress, etc.), and (2)
policy generation, where new policies are constructed by examining the
collection of existing policies.  Ultimately, we hope that this automation
enables control of policies by machines instead of administrators.
